Structured Versus Decorated Cospans

### 2020-11-23 cospans.tex
abstract's first take

\begin{document}
\begin{abstract}
\noindent
The first two authors have developed a compositional framework well-suited for studying networks that are built out of finite sets equipped 
with extra stuff. This framework, which goes by the name of `structured cospans', utilizes double categories where the objects are seen as 
inputs and outputs, horizontal 1-cells are `open networks', and 2-morphisms are maps between open networks. In this setup a functor $L \maps 
\A \to \textsf{X}$, which is typically a left adjoint, is used to replace the objects and vertical 1-morphisms of a given double category 
$\lX$ with the objects and morphisms, respectively, of the category $\A$. Horizontal 1-cells are then cospans in $\textsf{X}$ of a 
particular form with 2-morphisms given by maps of these cospans. Fong has also developed a similar framework utilizing cospans to study open 
networks which goes by the name of `decorated cospans'. In this setup, a lax monoidal functor $F \maps \A \to \textsf{Set}$ is used to 
`decorate' the apices of cospans in $\A$ with elements of $\textsf{Set}$ giving the cospans extra structure. Using a slight variation of 
Fong's framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax 
monoidal pseudofunctor using a well known construction of Grothendieck.
\end{abstract}

>>>>

\begin{document}
\begin{abstract}
The first two authors have recently developed a compositional framework by the name of `structured cospans' which is well-suited for studying networks.
This framework utilizes double categories where the objects are seen as inputs and outputs and horizontal 1-cells are ‘open networks’ written as cospans, where a typically left adjoint functor $L\maps \A\to\X$ is used to replace the objects and vertical 1-morphisms of a given double category $\lX$ with those of a category $\A$. Fong has also developed a similar framework utilizing cospans to study open networks which goes by the name of ‘decorated cospans’. In this setup, a lax monoidal functor $F\maps \A\to\Set$ is used to "decorate" the apices of cospans in $\A$ with elements of $\Set$ giving the cospans extra structure. Using a slight variation of Fong’s framework, we prove that these two frameworks are equivalent in the situation where a left adjoint can be obtained from a lax monoidal pseudofunctor using a well known construction of Grothendieck.
\end{abstract}
